### 2024-09-15 actuarial.qmd
20240915 - pundits
20240915 - videos

In general, many so-called experts are "pseudo-experts" who do not know the boundaries of their competence—that is, they do not know what they do not know; they have the illusion of validity of their predictions and are [overconfident](#sec-cognitiveBiasesOverconfidence) about their predictions [@Kahneman2011].
Yet, many people arrogantly proclaim to have predictive powers, including in low-validity environments such as fantasy football.
Indeed, pundits are more likely to be television guests if they are opinionated, clear, and (overly) confident and make big, bold predictions, because they are more entertaining [even though they tend to be less accurate than individuals whose thinking is more complex and less decisive; @Kahneman2011; @Silver2012].
[Optimism](#sec-cognitiveBiasesOptimism) and [(over)confidence](#sec-cognitiveBiasesOverconfidence) are valued by society [@Kahneman2011].
Nevertheless, true experts know their limits in terms of knowledge and ability to predict.

>>>>

In general, many so-called experts are "pseudo-experts" who do not know the boundaries of their competence—that is, they do not know what they do not know; they have the illusion of validity of their predictions and are [overconfident](#sec-cognitiveBiasesOverconfidence) about their predictions [@Kahneman2011].
Yet, many people arrogantly proclaim to have predictive powers, including in low-validity environments such as fantasy football.
Indeed, pundits are more likely to be television guests if they are opinionated, clear, and (overly) confident and make big, bold predictions, because they are more entertaining [even though they tend to be less accurate than individuals whose thinking is more complex and less decisive; @Kahneman2011; @Silver2012].
Consider sports pundits like Stephen A. Smith and Skip Bayless who make bold predictions with uber confidence.
[Optimism](#sec-cognitiveBiasesOptimism) and [(over)confidence](#sec-cognitiveBiasesOverconfidence) are valued by society [@Kahneman2011].
Nevertheless, true experts know their limits in terms of knowledge and ability to predict.

::: {.content-visible when-format="html:js"}

Here is a video of sports pundits, Stephen A. Smith and Skip Bayless, making bold statements and incorrect predictions:

![Video of Sports Pundits, Stephen A. Smith and Skip Bayless, Making Bold Statements and Incorrect Predictions. From: <https://www.youtube.com/watch?v=lTjBuEPcLlc>.](images/sportsPundits.mp4){width=100%}

### 2024-09-15 fantasy-football.qmd
20240915 - videos

![Video that Provides An Introduction to American Football.](images/football.mp4){width=100%}

@@

![Video that Provides an Introduction to Fantasy Football.](images/fantasyFootball.mp4){width=100%}

>>>>

![Video that Provides An Introduction to American Football. From: <https://www.youtube.com/watch?v=Ddwp1HyEFRE>.](images/football.mp4){width=100%}

@@

![Video that Provides an Introduction to Fantasy Football. From: <https://www.youtube.com/watch?v=XhrBapdhLEc>.](images/fantasyFootball.mp4){width=100%}
